Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-09-30 reviews.Rmd
Update reviews.Rmd
I don't think it was per se an oversight but it's a good thing to add indeed.

* Reviewer Concern: The manuscript lacked a discussion on HARKing, a practice detrimental to the integrity of hypothesis testing, and the error-statistical perspective emphasizing the importance of severe tests.
* Our Response: We acknowledged this oversight and added a dedicated section titled “Hacking, harking, and other harms” to address how our Bayesian framework addresses these concerns.

>>>>

* Reviewer Concern: The manuscript lacked a discussion on HARKing, a practice detrimental to the integrity of hypothesis testing, and the error-statistical perspective emphasizing the importance of severe tests.
* Our Response: We thank the reviewer for raising this issue. We added a dedicated section titled “Hacking, harking, and other harms” to address how our Bayesian framework addresses these concerns.
